---
title: "Deploying apps with {golem}'s `run_app()`"
output: github_document
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = FALSE)
```

When deploying [{golem}](https://github.com/ThinkR-open/golem) Shiny applications, the `run_app()` function is very critical but can be under appreciated/utilized (at least by me) for those new go {golem}. Here are some examples of how I have utilized `run_app()` in my apps.

# Specifying the server port

One handy customization of the `run_app()` function is the following, which allows you to specify what port to launch your application. In the following example, a default port number of 9999 is set, but this can be overridden when invoking the `run_app()` function. Personally, I like this because it allows me to bookmark 127.0.0.1:9999 in my browser, and quickly open up my application during development. This could also be useful in Docker deployments where the app port needs to be explicitly exposed (therefore, needs to be consistent).

```{r}
run_app <- function(
    port = 9999,
    ...
) {
    with_golem_options(
        app = shinyApp(ui = app_ui, 
                       server = app_server, 
                       options = list(port = port)), 
        golem_opts = list(...)
    )
}
```

# Parameterizing your application deployment

Some applications may benefit from having a parameter that specifies the deployment or some other runtime options. For example, a `view` parameter can be added to allow for customizing the application view at runtime. 

```{r}
run_app <- function(
    module = c("complete", "minimal"),
    ...
) {
    
    with_golem_options(
        
        # Using switch() to parameterize the app runtime
        app = switch(
            module,
            "complete" = shinyApp(
                ui = app_complete_ui, 
                server = app_complete_server
            ),
            "minimal" = shinyApp(
                ui = app_minimal_ui, 
                server = app_minimal_server
            )
        ), 
        golem_opts = list(...)
    )
}

```

This can also be helpful for loading in the correct configuration using the `config` package, which you can then pass to `golem_opts` and access throughout your app using `golem::get_golem_options()`.

```{r}
# run_app.R
run_app <- function(
    release = c("dev", "staging", "production"),
    ...
) {
    
    # Set config environment
    Sys.setenv("R_CONFIG_ACTIVE" = release)
    
    # Load in config
    config <- config::get(file = system.file("golem-config.yml",
                                             package = "golemApp"))
    
    with_golem_options(
        app = shinyApp(
            ui = app_ui, 
            server = app_server
        ), 
        golem_opts = list(config = config)
    )
}

# app_server.R 
app_server <- function(input, output, session){
    
    # Load config
    config <- golem::get_golem_options("config")
    
    ...
}

```

